%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Isfahan, Iran, 2021} % Job title DEEP LEARNING COURSE
    {Toxic comment classification on the dataset provided by Jigsaw/conversation AI.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementing a model that could classify all destructive comments on online forums or social media.}
      \end{cvitems}
    }
%---------------------------------------------------------
     \cventry
    {BACHELOR DEGREE PROJECT} % Job title
    {Sound power estimation with an acoustic camera (UMA-16 USB from MiniDsp Company).} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Different algorithms have been implemented on acoustic cameras in order to determine sound power estimation performance and sound source separation ability.}
      \end{cvitems}
    }
%-------------------------------------------------------

  \cventry
    {Isfahan, Iran, 2020 } % Job title
    {Creating an interface for automotive radars (ARS 408 from Continental Company).} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analysis, and validation of an mm-wave FMCW radar operation in a vehicle for detecting the presence of an occupant.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Isfahan, Iran, 2022} % Job title
    {Drone swarm simulation} % Organization
    {} % Location
    {} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Simulating a group of drones reaching from their origins to their destinations using the Gazebo simulator.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Isfahan, Iran, 2022} % Job title
    {Aerial imagery segmentation on Dubai's satellite imagery dataset.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementing U-Net model on TensorFlow for aerial imagery segmentation on unbalanced binary masks.}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Isfahan, Iran, 2022} % Job title
    {AI-driven snake game using deep Q learning with PyTorch.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This project was based on reinforcement learning which trained the snake to eat the food presented in the environment}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Isfahan, Iran, 2021} % Job title
    {Hybrid algorithm for disparity calculation based on semantic stereo matching.} % Organization
    {} % Location
    {} % Date(s)
    {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {}
    %   \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Isfahan, Iran, 2020} % Job title
    {Capuchin bird audio classification with TensorFlow.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementing a machine learning model to count the number of Capuchin bird calls within a given clip. }
      \end{cvitems}
    }





%---------------------------------------------------------
  \cventry
    {Isfahan, Iran, 2018} % Job title
    {Creating a signal generator with Verilog language on Xilinx Spartan-6 LX9.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming a signal generator with Verilog which is able to generate different waves on an FPGA using Vivado.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Isfahan, Iran, 2018} % Job title
    {Flappy bird game using Pygame module.} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Using Pygame, an open-source python library, for designing a fully functional game.}
      \end{cvitems}
    }

\end{cventries}
